\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing income inequality with tax data - Switzerland from 1917 to 2010}

### 2015-01-13 paper/subdocuments/results.Rnw
minor corrections results.Rnw

@@

# export nach stata (ungewichtet)
bern_habe <- rbind(habe11_bern,data.frame("income" = bern_kt2012$primeink2_hh/1000,"group"=1,"weight"=1))
bern_habe$group <- factor(bern_habe$group,labels=c("habe","tax"))
bern_habe <- bern_habe %>% mutate(income=ifelse(income<0,0,income))
write.dta(bern_habe, file="../../data/stata_data/bern_habe.dta")
# Ginis berechnen
gini_habe <- gini(bern_habe$income[bern_habe$group=="habe"],weights=bern_habe$weight[bern_habe$group=="habe"]); gini_habe
gini_tax <- gini(bern_habe$income[bern_habe$group=="tax"]); gini_tax
round(gini_habe-gini_tax,3)
# gini_tax-gini_habe diff=-0.069

>>>>

# Compare ginis for married among tax units and for HBS
round(gini(habe11.married$psteink,w=habe11.married$gew)-gini(bd.2011.ind),3)
# gini_tax-gini_habe diff=-0.066

@@

# export nach stata (ungewichtet)
bern_habe <- rbind(habe11_bern,data.frame("income" = bern_kt2012$primeink2_hh/1000,"group"=1,"weight"=1))
bern_habe$group <- factor(bern_habe$group,labels=c("habe","tax"))
bern_habe <- bern_habe %>% mutate(income=ifelse(income<0,0,income))
write.dta(bern_habe, file="../../data/stata_data/bern_habe.dta")
# Ginis berechnen
gini_habe <- gini(bern_habe$income[bern_habe$group=="habe"],weights=bern_habe$weight[bern_habe$group=="habe"]); gini_habe
gini_tax <- gini(bern_habe$income[bern_habe$group=="tax"]); gini_tax
round(gini_habe-gini_tax,3)
# gini_tax-gini_habe diff=-0.066
